---
title: 'Mountain climate review: guide to scripts'
author: "Adrienne Marshall"
date: "4/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
library(tidyverse)
```

# Get data from different sources. 

```{r scripts that get data}

# Get from web of science.
file.edit("get_recs.R")

# Get from crossref.
file.edit("crossref.Rmd")


# Unite all sources 
file.edit("aggregate_sources.R")


# Exclude data based on exclusions function - also uses river_names. 
file.edit("exclusions_fn.R")
file.edit("river_names.R")
```


# Assign reviewers.

## Assign reviewers for inclusion/exclusion stage.

```{r assign inclusion/exclusion reviewers}
file.edit("assignment2.R")
file.edit("assignment3.R")
file.edit("assignment4.R")
file.edit("assignment5.R")
file.edit("assignment6.R")
```

```{r aggregate data from inclusion/exclusion stage}
file.edit("final_corpus.R")
```

```{r calculate kappa from inclusion/exclusion}
file.edit("kappa_stats.R")
```



## Assign reviewers for the content analysis stage. 


```{r assign reviewers for content}
# First third: 
file.edit("assign_content_reviewers.R")

# Rest of the data: 
file.edit("assign_content_reviewers2.R")
```

# Analysis that doesn't require content analysis. 

```{r author networks}
file.edit("clean_author_data.R")
file.edit("network_analysis.Rmd")
file.edit("network_summary.Rmd") # shorter version

# Make some summary plots. 
file.edit("summary_plots.R")

# Identify the most prolific authors to manually get info for. 
file.edit("top_authors.R")
```


# Analyze findings from content analysis.

First, get our data from google sheets. You'll need to set up the `googlesheets` package to use this one effectively.

```{r get from google sheets}
source("get_from_google.R")

# Rename columns in a sane way.
source("rename_columns.R")

# Will also need to aggregate from multiple runs:
# file.edit("combine_content_analyses.R")

# Check arbitration. 
file.edit("check_arbitration.R")
```

We want to analyze across HUC6 units - so make a HUC6 layer: 

```{r huc6 layer}
file.edit("get_huc6.R")
```


Look at some initial exploratory work: 

```{r initial exploratory}
file.edit("content_analysis.Rmd") # could move into old. 
```

Figure 2: Number of papers over time
```{r papers over time}
file.edit("papers_over_time.R")
```

Figure x: Bar chart of spatial extents
```{r spatial extents bar chart}
file.edit("extents_bar_chart.R")
```


Figure 8: HUC6 maps
```{r huc6_maps.R}
file.edit("huc6_maps.R") # might be better to just use this to make data, and make a map in QGIS?
file.edit("studies_per_huc.R")
file.edit("huc6_heatmaps.R")
```

