---
title: 'Mountain climate review: guide to scripts'
author: "Adrienne Marshall"
date: "10/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = F)
library(tidyverse)
```

# Get data from different sources. 

```{r scripts that get data}

# Get from web of science.
file.edit("get_recs.R")

# Get from crossref.
file.edit("crossref.Rmd")


# Unite all sources 
file.edit("aggregate_sources.R")


# Exclude data based on exclusions function - also uses river_names. 
file.edit("exclusions_fn.R")
file.edit("river_names.R")
```


# Assign reviewers.

## Assign reviewers for inclusion/exclusion stage.

```{r assign inclusion/exclusion reviewers}
file.edit("assignment2.R")
file.edit("assignment3.R")
file.edit("assignment4.R")
file.edit("assignment5.R")
file.edit("assignment6.R")
```

```{r aggregate data from inclusion/exclusion stage}
file.edit("final_corpus.R")
```

```{r calculate kappa from inclusion/exclusion}
file.edit("kappa_stats.R")
```


## Assign reviewers for the content analysis stage. 

```{r assign reviewers for content}
# First third: 
file.edit("assign_content_reviewers.R")

# Rest of the data: 
file.edit("assign_content_reviewers2.R")
```

# Analysis that doesn't require content analysis. 

```{r author networks}
file.edit("clean_author_data.R")
file.edit("network_analysis.Rmd")
file.edit("network_summary.Rmd") # shorter version

# Make some summary plots. 
file.edit("summary_plots.R")

# Identify the most prolific authors to manually get info for. 
file.edit("top_authors.R")
```


# Analyze findings from content analysis.

## Get and clean our coded data: 

First, get our data from google sheets. You'll need to set up the `googlesheets` package to use this one effectively.

```{r get from google sheets}
source("get_from_google.R")

# Rename columns in a sane way.
# Also combines arbitrated data from rounds 1 and 2. 
source("rename_columns.R")

# Will also need to aggregate from multiple runs:
# file.edit("combine_content_analyses.R")

# For Round 1:-----------------
# Check arbitration. 
file.edit("check_arbitration.R")

# For Round 2: ---------------
# Check agreement (before arbitration): 
file.edit("check_agreement2.R")

# Check arbitration. ----------
file.edit("check_arbitration_all.R")

# Unite both rounds. ---------
# Currently, some have different values (e.g., hucs)
file.edit("unite_rounds.R")

# Get summary statistics.
file.edit("summary_stats.R")

# Get abstracts for our final corpus. 
file.edit("get_abstracts.R")

```

We want to analyze across HUC6 units - so make a HUC6 layer: 

```{r huc6 layer}
file.edit("get_huc6.R")
```

## Analyze and visualize the coded data: 

Figure 2: Number of papers over time
```{r papers over time}
file.edit("papers_over_time.R")
```

Figure 3. Simple characterization of paper topics, disciplines, and IAM (impacts/adaptation/mitigation).
```{r content bar charts}
file.edit("topical_bar_charts.R")
```


Figure 4. Topics and disciplines covered by impacts, adaptation, and mitigation: 
```{r IAM*topic}
file.edit("IAM_topic_discipline.R") # makes both a bar chart and radar. Set discipline vs topic at top. 
file.edit("topic_discipline_radar.R")
```

Figure x. Topics and disciplines subset by extent? 
```{r extent*topic}
file.edit("extent_topic_discipline.R")
```


Figure x. Network map of topics; network map of disciplines. 
```{r topic network map}
file.edit("topic_network_map.R")
file.edit("discipline_network_map.R")

# Make network heatmaps of topics, subset by discipline:
file.edit("discipline_topic_heatmaps.R")
```

Figure x. Topic interactions over time. 
```{r topics interactions over time}
file.edit("topic_interactions_time.R")
```


Figure 8: HUC6 maps
```{r huc6_maps}
file.edit("studies_per_huc.R") # total number of studies per HUC. 
file.edit("huc6_maps.R") # maps by topic, discipline, and HUC.
file.edit("huc6_heatmaps.R")

file.edit("huc6_topic_discipline.Rmd")
```


Figure x: Simple characterization of spatially-relevant factors: biome and extent.
HUC-6 is not included because it is mapped in separate figures. 
```{r spatial extents bar chart}
file.edit("spatial_bar_charts.R")
```

Potential figure: map points. 
This could potentially get laid over a HUC6 map? Not sure the best way to integrate. 
```{r point map}
file.edit("point_map.R")
```

Write matrices to be used in factor/PCA analyses. 
```{r create matrices}
file.edit("make_matrices.R")
```

Make a bar graph of future versus observed impacts by discipline. 
```{r future observed disciplines}
file.edit("future_observed_disciplines.R")
```


